Harris County, Texas residents faced several barriers to voter identification access during the 2016 United States election

### 2024-02-13 paper/paper.qmd
Corrected a minor issue in the paper

Since this analysis exclusively focuses on the voter-level RID-filer data, which could only be accessed by the authors through a formal request [@voterid], other similar datasets could not be used to generate this report. After downloading the data with the R programming language [@citeR] and the `tidyverse` [@citetidyverse], `haven` [@citehaven], and `labelled` [@citelabelled] packages, the `tidyverse` [@citetidyverse] package was employed in order to clean and filter the data. In doing so, a new variable was created to indicate whether or not each individual was White. Finally, the `tidyverse` [@citetidyverse] and `here` [@citehere] packages were used to load the data into the R programming language [@citeR], and the `tidyverse` [@citetidyverse] package was used to create the graph in this section.

>>>>

Since this analysis exclusively focuses on the voter-level RID-filer data, which could only be accessed by the authors through a formal request [@voterid], other similar datasets could not be used to generate this report. After downloading the data with the R programming language [@citeR] and the `tidyverse` [@citetidyverse], `haven` [@citehaven], and `labelled` [@citelabelled] packages, the `tidyverse` [@citetidyverse] package was employed in order to clean and filter the data. In doing so, a new variable was created to indicate whether or not each individual was White. Finally, the `tidyverse` [@citetidyverse] and `here` [@citehere] packages were used to load the data with the R programming language [@citeR], and the `tidyverse` [@citetidyverse] package was used to create the graph in this section.
